% ************************** Thesis Acknowledgements **************************

\begin{acknowledgements}      

I am very grateful to the Centre for Doctoral Training (CDT) in Diamond Science and Technology (DST) at Warwick University, and the EPSRC for funding this project opportunity. Additional COVID-19 support from the DST CDT allowed me to continue experimental characterisation of emitter structures, substantially improving the quantity of primary data collected and mitigating the unprecedented delay that COVID-19 had on my experimental work. The coincidental timing of the lockdown starting just as I was preparing for experimental training posed a significant challenge.

I would like to thank my supervisors, Prof. Jon Goss and Prof. Nick Wright. While it is quite natural (hopefully) for PhD students to laud their supervisors impact on their work, I can say with confidence that I would never have been able to complete the work required for a PhD without the insight, support, and all-round expertise that both Jon and Nick have provided for me. Though Jon's red or green pen has made me reconsider whether or not I can write in English anymore. Vielleicht sollte ich mehr Deutsch lernen, um es Jon schwerer zu machen, Fehler zu finden.

Further thanks go to Dr. Patrick Salter and Dr. Ravi Shivaraman, who were able to provide a one of a kind laser processed sample based on my conceptual designs, that proved to be an excellent case study. The future of laser processed diamond devices appears to hold a lot of promise. 

This work would not have been possible without the material support of phosphorous doped diamond, and general wisdom offered by Evince Technology Ltd. Dr. Gareth Taylor, Dr. Paul Farrar and Dr. Hassan Ganjitabar all had a significant impact on my development as a researcher, laying the foundations I needed to progress with this endeavour.

I would also like to thank my peers within the Newcastle University power electronic group, who helped me with clean room and characterisation training. Dr. Johannes Gausden in particular was deeply helpful during this process.

Finally I would like to acknowledge those who perhaps don't need mentioning. John and David - thanks for helping with some proof reading and everything else along the way. My mum and dad, all of those who have been supportive at Climb Newcastle and Matthew for the trips out and mutual support as we both made our ways through a PhD.
\end{acknowledgements}
